---
output: rmarkdown::github_document
---

# freebase

A 'usethis'-like Package for Base Pseudo-equivalents of 'tidyverse' Code

## Description

The 'tidyverse' is awesome, but can take a bit compile on systems
where there are no pre-built binary packages. Methods are provided which use
the facilities of the 'usethis' package to snap-in base versions of useful
'tidyverse' functions that are mostly equivalent (some are more complete
than others). The base R counterpart functions will likely be slower than
the 'tidyverse' equivalents but using them will decrease 'Imports' 
dependencies. 

Use deliberately and with caution.
    
## What's Inside The Tin

The following functions are implemented:

- `use_detect`:	Use base-ified equivalents of "detect"-ors (these support `~{}` formula functions)
- `use_infix_helpers`:	Use infix-helpers
- `use_isers`:	Use "is_" functions
- `use_keepers`:	Use base-ified equivalents of keep/discard/compact (these support `~{}` formula functions)
- `use_mappers`:	Use base-ified equivalents of 'map'-pers (these support `~{}` formula functions)
- `use_safely`:	Use base-ified equivalents of "safely"-ifiers
- `use_tidylite()`:	Use base R versions of 'tidyr' 'gather'/'spread'
- `use_walkers`:	Use base-ified equivalents of keep/discard/compact (these support `~{}` formula functions)

## Installation

```{r eval=FALSE}
devtools::install_github("hrbrmstr/freebase")
```

```{r message=FALSE, warning=FALSE, error=FALSE, include=FALSE}
options(width=120)
```

## Usage

```{r message=FALSE, warning=FALSE, error=FALSE}
library(freebase)

# current verison
packageVersion("freebase")

```

